TBD

### 2021-02-21 outputs/paper/paper.Rmd
Add tables for Chi-squared tests

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
library(purrr)
#devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)

all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
```

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####

### Format percent
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}

### Format table for Chi-squared test
tableChisq <- function(stat, df, p) {   
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, chi_p)

  kable(chi_df,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    kable_paper(c("striped", "hover"))
}

```

@@

```{r regions, echo = FALSE, message = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
dfBoroughs <- dfBoroughs[-c(10),]
# print(dfBoroughs)

### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y", start = 0) +
  geom_text(aes(x=1.65, y = ypos, label = percent(prop)), color = "black", size=2.8) +
  scale_fill_manual(values=lacroix_palette("PeachPear", n = 9)) + 
  labs(fill = "Region", title = "Proportion of Restaurants in Toronto by Borough") +
  theme(plot.title = element_text(face = "bold")) +
  theme_void() +
  theme(plot.title = element_text(face = "bold"))
```

@@

```{r Q11, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None

ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity (most orders)",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?

t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))

t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)

total <- merge(t1, t2, by = c("type"))

kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))

### T-Tests (Welch's)

#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)

#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)

#Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy)
t_tests = subset(t_tests, select = -c(alternative, method, conf.low, conf.high))
t_tests %>%  
  kable(
    col.names = c("Mean of the Differences",
                  "Mean (Employees Before Intervention)",
                  "Mean (Employees Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ")) %>%
  kable_paper(c("striped", "hover")) %>%
  landscape()

```

@@

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type)
chisq.test(q7_chi)
```

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type)
chisq.test(q8_chi)
```

@@

```{r Q10, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

q10_chi <- table(all_simulated_dataset$Q10, all_simulated_dataset$type)
chisq.test(q10_chi)
```

@@

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type)
chisq.test(q12_chi)
```

```{r Q13, echo = FALSE, message = FALSE}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more

ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = str_wrap("Percentage of hours reduced between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q14, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in Days of Operation",
       y = "# of Restaurants",
       title = str_wrap("Reduction of operating days between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()

tableChisq(q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

```{r Q15, echo = FALSE, message = FALSE}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable

### bar graph/pie chart/line

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Days Reduced",
       y = "# of Restaurants",
       title = "Reduction in days of operation per week",
       fill = "Condition") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q16, echo = FALSE, message = FALSE}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding Applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
library(dplyr)
library(palettetown)
library(RColorBrewer)
library(ggthemes)
library(scales)
library(broom)
library(purrr)
#devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)
all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
```

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####
### Format percent
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
### Format table for Chi-squared test
tableChisq <- function(capt, stat, df, p) {   
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, paste(chi_p,"*"))

  kable(chi_df,
        digits = 2,
        caption = capt,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level") %>%
    kable_paper(c("striped", "hover"))
}
```

@@

```{r regions, echo = FALSE, message = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
dfBoroughs <- dfBoroughs[-c(10),]
# print(dfBoroughs)
### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  coord_polar("y", start = 0) +
  geom_text(aes(x=1.65, y = ypos, label = percent(prop)), color = "black", size=2.8) +
  scale_fill_manual(values=lacroix_palette("PeachPear", n = 9)) + 
  labs(fill = "Region", title = "Proportion of Restaurants in Toronto by Borough") +
  theme(plot.title = element_text(face = "bold")) +
  theme_void() +
  theme(plot.title = element_text(face = "bold"))
```

@@

```{r Q11, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31, which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None
ggplot(data = all_simulated_dataset, mapping = aes(x = Q11, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("UberEats", "SkiptheDishes", "DoorDash", "In-house delivery service", "Other", "None")) +
  labs(x = "Delivery Service",
       y = "# of Restaurants",
       title = "Food courier service popularity (most orders)",
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) + 
  theme_fivethirtyeight()
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)
#Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy)
t_tests = subset(t_tests, select = -c(alternative, method, conf.low, conf.high))
t_tests %>%  
  kable(
    col.names = c("Mean of the Differences",
                  "Mean (Employees Before Intervention)",
                  "Mean (Employees Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ")) %>%
  kable_paper(c("striped", "hover")) %>%
  landscape()
```

@@

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q7", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q8", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

@@

```{r Q10, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q10_chi <- table(all_simulated_dataset$Q10, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q10", q10_chi$statistic, q10_chi$parameter, q10_chi$p.value)
```

@@

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q12", q12_chi$statistic, q12_chi$parameter, q12_chi$p.value)
```

```{r Q13, echo = FALSE, message = FALSE}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more
ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = str_wrap("Percentage of hours reduced between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q14, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No 
ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in Days of Operation",
       y = "# of Restaurants",
       title = str_wrap("Reduction of operating days between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q14", q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

```{r Q15, echo = FALSE, message = FALSE}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable
### bar graph/pie chart/line
ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Days Reduced",
       y = "# of Restaurants",
       title = "Reduction in days of operation per week",
       fill = "Condition") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q16, echo = FALSE, message = FALSE}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding Applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```
